\documentclass[10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{combelow}
\usepackage{fullpage}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{microtype} 
\usepackage[usenames,dvipsnames]{color}
\usepackage[english]{babel}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\linespread{1.2}

% \renewcommand{\familydefault}{cmr}

% \definecolor {Primary}{RGB}{176,196,222}
\definecolor {Primary}{HTML}{4169e1}
\definecolor {Link}{HTML}{4682b4}
% \definecolor {Link}{RGB}{0,72,228}

\textwidth 6.6in
\textheight 8.5in

\oddsidemargin 0in
\evensidemargin 0in

\hypersetup{ 
  colorlinks=true, 
  linkcolor=Link,
  filecolor=Link,
  citecolor=Link,
  urlcolor=Link,
}

\begin{document}
\noindent
\textcolor{Primary}{\textbf {\huge {\textsc{Bogdan Balan}}}}

\vspace{0.16in}
\noindent
Senior Software Engineer \\
+41 (0) 765 -- 707 -- 360\\
\href{mailto:bcqdan@gmail.com}{bcqdan@gmail.com}

\vspace{0.32in}
\noindent
\textcolor{Primary}{{\large \textsc{Mission, Values}}}

\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}

\item
{\bf Build exceptional products and services that have a positive impact on the world.}
\item
Focus on the user -- is the first principle that guides my thinking and decisions.
\item
Leadership is about exercising good judgement, building strong work relationships based on trust, prioritizing the mission and the team.
\item
High quality standards matter, for code, product, communication, documentation, and everything else.

\end{list}

\vspace{0.16in}
\noindent
\textcolor{Primary}{{\large \textsc{Experience}}}
\begin{list}{\labelitemii}{\leftmargin=0em}

\item
{\bf Personal Projects -- 2022--2023.}\\
On a personal leave for a few months, studied Swift, SwiftUI, launched some hobby apps, \href{https://apps.apple.com/us/app/sudoku-black-belt/id1639802667}{Sudoku Black Belt} and 
\href{https://apps.apple.com/us/app/stim-tally/id6444342899}{Stim Tally}.

\item
{\bf Stripe -- SEPA and Bacs Direct Debit Payment Methods -- Senior Engineer -- 2022.}\\
Engineering Lead on the Reliability team for European Direct Debit payment methods at Stripe. Drove an effort to reduce engineering toil spent offering support to customers.
  
\item
{\bf Google Switzerland -- YouTube Movies and Shows -- Senior Engineer -- 2011--2022.}\\
Engineering Lead on Playback Reliability for premium content. Led an effort to setup playback metrics and ran large scale analysis of playback quality across mobile, TV and Web players.

\item
{\bf Google Switzerland -- Tasks iOS App -- Technical Lead Manager -- 2017--2021.}\\
Wrote the first version of Tasks iOS app as the only engineer on the team, then built and lead the iOS engineering team.
Contributed to the technical direction of the overall Tasks service stack, impacting Android and Web surfaces
as well. Integrated Tasks in Calendar, Gmail and Meet on iOS.
  
\item
{\bf Google UK -- Docs, Sheets, Slides Android -- Technical Lead Manager -- 2014--2016.}\\
Added support for working with Office formats (docx, xlsx, pptx) to Docs, Sheets, Slides Android Apps. Spined off a
sub-team to contribute directly to Android SDK (to improve text support such as RTL, dynamic fonts). 

\item
{\bf Google UK -- Google Offers Android App -- Technical Lead Senior Engineer -- 2012}.\\
Lead the development of Google Offers on Android, including integrations with Google Maps and Google Wallet.
Re-architected the app from a WebView embedding HTML to a fully native stack.

\item
{\bf Google UK -- YouTube Android App -- Software Engineer -- 2009--2012.}\\
Wrote large parts of the YouTube Android App such as player controls, related videos, comments, parts of the UI 
infrastructure, such as support for swipeable tabs.
Before Android, contributed to Symbian and Windows Mobile YouTube Apps.

\item
{\bf Google Poland -- Web--Search Infrastructure -- Software Engineer -- 2007--2009.}\\
Worked on expanding the size of the search index, in the area of quality, running experiments to ensure
search results from a larger index add benefit to users.

\item
{\bf Various Companies -- Software Engineer -- 2001--2007.}\\
Prior to Google, I worked as a Software Engineer at small to medium sized companies in Romania, mostly in Java / J2EE projects:
Oc\'e, Intrasoft--International, Waterford Institute of Technology (NGO), ArtSoft--Consult, Caatoosee.

\end{list}

% \newpage

\vspace{0.16in}

\noindent
\textcolor{Primary}{{\large \textsc{Education}}}
\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item Polytechnics University, Computer Science Faculty, Timi\cb{s}oara, Romania, 2001--2003, Uncompleted.
  \item West University, Mathematics and Informatics Faculty, Timi\cb{s}oara, Romania, 2003--2004, Uncompleted.
  \item High School of Informatics Grigore Moisil, Timi\cb{s}oara, Romania, 2007--2011.
  \item University College London, Physics Department, Evening Astronomy Course, 2011.
\end{list}

\vspace{0.16in}

\noindent
\textcolor{Primary}{{\large \textsc{Awards and Distinctions}}}
\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item{Second Prize, National Olympiad of Informatics, Romania, 2000.}
  \item{Third Prize, National Olympiad of Informatics, Romania, 2001.}
  \item{First Prize, Regional Olympiad of Informatics, Timi\cb{s}, Romania 2000.}
  \item{Second Prize, Regional Programming Contest, Timi\cb{s}, Romania 2001.}
  \item{Second Prize, Regional Projects Contest, Timi\cb{s}, Romania 2001.}
\end{list}

\vspace{0.16in}

\noindent
\textcolor{Primary}{{\large \textsc{Volunteer Work}}}
\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item{Teacher, Olympiad Training, High School of Informatics Grigore Moisil, Timi\cb{s}oara, Romania 2002, 2003, 2004.}
  \item{Jury Member, Subjects Author, Regional Olympiad of Informatics, Timi\cb{s}oara, Romania, 2002, 2003.}
\end{list}

\vspace{0.16in}

\noindent
\textcolor{Primary}{{\large \textsc{Technologies}}}
\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item{Objective C, Java, Python, C/C++, Haskell, JavaScript, Bash Script, SQL, etc.}
  \item{UIKit, Android SDK.}
  \item{Git, Mercurial.}
  \item{MacOS, Linux.}
\end{list}

\vspace{0.16in}

\noindent
\textcolor{Primary}{{\large \textsc{Leadership}}}
\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item{Technical Leadership.}
  \item{People Management and Mentoring.}
  \item{Project Management.}
  \item{Prioritization and Strategy.}
  \item{Interviewing and Recruiting.}
\end{list}

\vspace{0.16in}

\noindent
\textcolor{Primary}{{\large \textsc{Hobbies}}}
\begin{list}{\labelitemii}{\leftmargin=0em}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
  \item{Programming, Algorithmic Puzzles.}
  \item{Knife Sharpening, Cooking.}
  \item{Rubik Cube - Speed Solving}
\end{list}

\end{document}
